Developing a preprint culture in biology

### 2012-10-05 ms.tex
Tightening the Introduction

Public preprint servers allow authors to make manuscripts publicly available
before, or in parallel to, submitting them to journals for traditional
peer-review. The rationale for preprint servers is fundamentally simple: to make
the results available to the scientific community as soon as possible rather
than to wait until the peer-review process is fully completed. The goal of arXiv
and open preprint servers is not to circumvent the peer-review process; almost all
manuscripts on arXiv are submitted to peer-review.  Sharing ideas as quickly as
possible using preprint servers has numerous advantages.  These include rapid
dissemination of work-in-progress to a wider audience, including readers in
developing countries where access to subscription journals is often a limiting
factor in scientific research.  Furthermore, preprints provide the opportunity
to solicit feedback from a larger pool of reviewers and can be seen as an
integral aspect of a vigorous peer-review process \cite{hoc12}.  Preprint
servers therefore increase the number of opportunities for review and revision
prior to publication, resulting in higher quality submissions and also could
alleviate reviewer burden.

Preprints gained popularity 20 years ago with the advent of arXiv, an open
preprint server widely used in physics and mathematics \cite{gin11}. Preprints
are also integral to the culture of other scientific fields.  Paul Krugman noted
that, in economics, the \emph{traditional model of submit, get refereed,
publish, and then people will read your work broke down a long time ago. In
fact, it had more or less fallen apart by the early 80s} \cite{kru12}. In
addition to a section in arXiv, economists have also the RePEc (Research Papers
in Economics) initiative, which aims to create an archive of working papers,
manuscripts, and book chapters.  Despite the success of this approach in other
fields, most manuscripts in biology are not submitted to a public archive before
being submitted to peer-review.  In this article, we first highlight the
advantages of open preprint servers for both scientists and publishers. We
then debunk a few misconceptions, discuss the policies of major publishers in
biology, and briefly review the most popular open preprint servers currently available.

>>>>

Public preprint servers allow authors to make manuscripts publicly available
before, or in parallel to, submitting them to journals for traditional
peer-review. The rationale for preprint servers is fundamentally simple: to make
the results of scientific research available to the scientific community as soon
as possible, instead of waiting until the peer-review process is fully completed.
Sharing manuscripts using preprint servers has numerous advantages including: 1) rapid
dissemination of work-in-progress to a wider audience; 2) improved peer review by
encouraging feedback from the entire research community;
and 3) a fair and straightforward way to establish precedence.

Preprints began to gain popularity 20 years ago with the advent of arXiv, an open
preprint server widely used in physics and mathematics \cite{gin11}. Preprints
are also integral to the culture of other scientific fields.  Paul Krugman noted
that, in economics, the \emph{traditional model of submit, get refereed,
publish, and then people will read your work broke down a long time ago. In
fact, it had more or less fallen apart by the early 80s} \cite{kru12}. In
addition to a section in arXiv, economists have also the RePEc (Research Papers
in Economics) initiative, which aims to create an archive of working papers,
manuscripts, and book chapters.

Despite the success of this approach in other
fields, most manuscripts in biology are not posted to preprint servers and
are therefore not seen by more than a handful of other scientists prior to
publication. In this article, we: 1) highlight the
advantages of open preprint servers for both scientists and publishers; 2)
address several misconceptions about preprints that are common among biologists;
3) discuss the preprint policies of major publishers in biology;
and 4) review the most popular preprint servers currently available.
